\thesistitle

### 2025-07-23 manuscript/main.tex
fix name

%=== Metadata ===
\newcommand{\thesistitle}{VS Code Language Extension - MiniProb}
\newcommand{\authorname}{Rafael Tanzer}
\newcommand{\supervisor}{Michele Chiaria, Simone , Francesco Pontigia and Ezzio Bartocci}
\newcommand{\institution}{TU Vienna}
\newcommand{\department}{Cyber-Physical Systems$_{E191-01}$}
\newcommand{\logoimage}{graphics/logo.png} % Path to your logo image
\newcommand{\submissionmonth}{May}
\newcommand{\submissionyear}{2025}
\newcommand{\submissionday}{24}

@@

  \vspace*{0.5cm}
  \noindent
  \begin{tabular}{@{}r @{\quad} l@{}}
    Betreuung: & Ezzio Bartocci\\
    Mitwirkung: & Michele Chiari\\
              & Francesco Pontiggia
  \end{tabular}

@@

  \noindent
  \makebox[\textwidth]{%
    {\small Wien, \submissionday~\submissionmonth~\submissionyear}%
    \hfill
    \begin{tabular}[t]{@{\hspace{2cm}}c@{\hspace{0.2cm}}c@{}}
      \rule{5cm}{0.4pt} & \rule{5cm}{0.4pt} \\[-0.3ex]
      {\small \authorname} & {\small Ezzio Bartocci}
    \end{tabular}%
  }
\end{titlepage}

@@

  \noindent
  \makebox[\textwidth]{%
    {\small Vienna, \submissionday~\submissionmonth~\submissionyear}%
    \hfill
    \begin{tabular}[t]{@{\hspace{2cm}}c@{\hspace{0.2cm}}c@{}}
      \rule{5cm}{0.4pt} & \rule{5cm}{0.4pt} \\[-0.3ex]
      {\small \authorname} & {\small Ezzio Bartocci}
    \end{tabular}%
  }
\end{titlepage}

@@

\noindent I would like to thank my supervisory team - Michele Chiari, Francesco Pontiggia and Ezzio Bartocci - for generously sharing their expertise throughout this project.
Their patient guidance on implementation details, contextual foundations, and domain-specific nuances of the application was invaluable. Whenever I encountered a technical
hurdle or needed deeper insight into the domain, they were always ready with thoughtful advice and resources.
\vspace{1ex}
\noindent I would also like to acknowledge the use of ChatGPT 4o-mini-high during the preparation of this thesis. I used it to enhance my writing by correcting grammar
and spelling errors, as well as improve the overall tone and wording.
Furthermore, the AI-tools was used as a consultation on common topics and for creating the Biblatex citations.
All final texts and substantive content, however, reflect my own efforts and have been critically reviewed by me.
\clearpage

>>>>

%=== Metadata ===
\newcommand{\thesistitle}{VS Code Language Extension - MiniProb}
\newcommand{\authorname}{Rafael Tanzer}
\newcommand{\supervisor}{Michele Chiaria, Simone , Francesco Pontigia and Ezio Bartocci}
\newcommand{\institution}{TU Vienna}
\newcommand{\department}{Cyber-Physical Systems$_{E191-01}$}
\newcommand{\logoimage}{graphics/logo.png} % Path to your logo image
\newcommand{\submissionmonth}{May}
\newcommand{\submissionyear}{2025}
\newcommand{\submissionday}{24}

@@

  \vspace*{0.5cm}
  \noindent
  \begin{tabular}{@{}r @{\quad} l@{}}
    Betreuung: & Ezio Bartocci\\
    Mitwirkung: & Michele Chiari\\
              & Francesco Pontiggia
  \end{tabular}

@@

  \noindent
  \makebox[\textwidth]{%
    {\small Wien, \submissionday~\submissionmonth~\submissionyear}%
    \hfill
    \begin{tabular}[t]{@{\hspace{2cm}}c@{\hspace{0.2cm}}c@{}}
      \rule{5cm}{0.4pt} & \rule{5cm}{0.4pt} \\[-0.3ex]
      {\small \authorname} & {\small Ezio Bartocci}
    \end{tabular}%
  }
\end{titlepage}

@@

  \noindent
  \makebox[\textwidth]{%
    {\small Vienna, \submissionday~\submissionmonth~\submissionyear}%
    \hfill
    \begin{tabular}[t]{@{\hspace{2cm}}c@{\hspace{0.2cm}}c@{}}
      \rule{5cm}{0.4pt} & \rule{5cm}{0.4pt} \\[-0.3ex]
      {\small \authorname} & {\small Ezio Bartocci}
    \end{tabular}%
  }
\end{titlepage}

@@

\noindent I would like to thank my supervisory team - Michele Chiari, Francesco Pontiggia and Ezio Bartocci - for generously sharing their expertise throughout this project.
Their patient guidance on implementation details, contextual foundations, and domain-specific nuances of the application was invaluable. Whenever I encountered a technical
hurdle or needed deeper insight into the domain, they were always ready with thoughtful advice and resources.
\vspace{1ex}
\noindent I would also like to acknowledge the use of ChatGPT 4o-mini-high during the preparation of this thesis. I used it to enhance my writing by correcting grammar
and spelling errors, as well as improve the overall tone and wording.
Furthermore, the AI-tools was used as a consultation on common topics and for creating the Biblatex citations.
All final texts and substantive content, however, reflect my own efforts and have been critically reviewed by me.
\clearpage
